---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```



<!-- badges: start -->
  [![R build status](https://github.com/marius-cp/calibrationband/workflows/R-CMD-check/badge.svg)](https://github.com/marius-cp/calibrationband/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/calibrationband)](https://CRAN.R-project.org/package=calibrationband)
<!-- badges: end -->
  
# calibrationbands

An R package to assess calibration of binary outcome predictions. Authored by Timo Dimitriadis (Heidelberg University), Alexander Henzi (University of Bern), and Marius Puke (University of Hohenheim). 
  
## Installation

calibrationband is available on [The Comprehensive R Archive Network (CRAN)](https://cran.r-project.org/package=calibrationband).

```{r, eval = FALSE}
install.packages("calibrationband")
```

### Development version

The most current version is available from GitHub.

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("marius-cp/calibrationband")
```

## Example

```{r example, warning=F, message=F}
library(calibrationband)
library(dplyr)
set.seed(123)
s=.8
n=10000
x <- runif(n)
p <- function(x,s){p = 1/(1+((1/x*(1-x))^(s+1)));return(p)}
dat <- tibble::tibble(pr=x, s=s, cep = p(pr,s), y=rbinom(n,1,cep))%>% dplyr::arrange(pr)

cb <- calibration_bands(x=dat$pr, y=dat$y,alpha=0.05, method = "round", digits = 3)
print(cb) # prints autoplot and summary, see also autoplot(.) and summary(.)
```
Use `ggplot2:autolayer` to customize the plot. 
```{r}
autoplot(cb,approx.equi=500, cut.bands = F,p_isoreg = NA,p_ribbon = NA,p_diag = NA)+
  ggplot2::autolayer(
    cb,
    cut.bands = F,
    p_diag = list(low = "green", high = "red", guide = "none", limits=c(0,1)),
    p_isoreg = list(linetype = "dashed"),
    p_ribbon = list(alpha = .1, fill = "red", colour = "purple")
                     )
```


